---
title: "ETC2420/5242 Assignment 2"
subtitle: "Group [X] - [Your Group Name]"
author: 
  - "Student Name 1 (Student ID)"
  - "Student Name 2 (Student ID)"
  - "Student Name 3 (Student ID)"
  - "Student Name 4 (Student ID)"
date: "13 October 2025"
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    colorlinks: true
    geometry:
      - margin=2.5cm
    fontsize: 11pt
execute:
  echo: true
  warning: false
  message: false
  eval: true
---

```{r setup}
#| include: false
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,
                      eval = TRUE, message = FALSE)
```

```{r load-packages}
# Load required packages
library(tidyverse)
library(here)
# Add other packages as needed
```

```{r load-data}
# Load data files
# data <- read_csv(here("data", "filename.csv"))
```

\newpage

# Task 1: \[Task Title\]

## Introduction

<!-- Provide a brief overview of Task 1 and your approach -->

## Data Exploration

```{r task1-exploration}
# Exploratory analysis code

```

<!-- Describe what you found in your exploration -->

## Analysis

### Technical Approach

<!-- Describe the statistical methods and techniques you will use -->

```{r task1-analysis}
# Main analysis code

```

### Results

<!-- Present your results with appropriate visualizations -->

```{r task1-plots}
# Create visualizations

```

**Figure 1.1:** \[Caption describing the plot\]

<!-- Interpret the results technically -->

## Interpretation

<!-- Non-technical explanation of your findings -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 1 -->

\newpage

# Task 2: \[Task Title\]

## Introduction

<!-- Provide a brief overview of Task 2 and your approach -->

## Data Preparation

```{r task2-data-prep}
# Data wrangling and preparation

```

## Analysis

### Technical Approach

<!-- Describe your methodology -->

```{r task2-analysis}
# Main analysis code

```

### Results

```{r task2-results}
# Generate results and visualizations

```

**Figure 2.1:** \[Caption describing the plot\]

<!-- Technical interpretation of results -->

## Interpretation

<!-- Non-technical explanation for a general audience -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 2 -->

\newpage

# Task 3: \[Task Title\]

## Introduction

<!-- Overview of Task 3 -->

## Methodology

### Data Processing

```{r task3-data}
# Data processing code

```

### Statistical Methods

<!-- Explain the statistical techniques used -->

```{r task3-methods}
# Implementation of statistical methods

```

## Results and Visualizations

```{r task3-plots}
# Create visualizations

```

**Figure 3.1:** \[Caption\]

### Technical Analysis

<!-- Technical interpretation -->

### Non-Technical Summary

<!-- Explain findings in accessible language -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 3 -->

\newpage

# Task 4: \[Task Title\]

## Introduction

<!-- Overview of Task 4 -->

## Analysis Approach

### Data Exploration

```{r task4-exploration}
# Exploratory analysis

```

### Statistical Analysis

<!-- Describe your analytical approach -->

```{r task4-analysis}
# Main analysis code

```

## Results

```{r task4-results}
# Results and visualizations

```

**Figure 4.1:** \[Caption\]

### Technical Findings

<!-- Technical interpretation of results -->

### Practical Implications

<!-- Non-technical explanation and real-world implications -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 4 -->

\newpage

# Task 5: \[Task Title\]

## Introduction

<!-- Overview of Task 5 -->

## Comprehensive Analysis

### Data Integration

```{r task5-data-integration}
# Combining and processing data

```

### Analytical Framework

<!-- Describe your comprehensive approach -->

```{r task5-framework}
# Implementation of analytical framework

```

## Results and Insights

```{r task5-results}
# Generate comprehensive results

```

**Figure 5.1:** \[Caption\]

### Technical Analysis

<!-- Detailed technical interpretation -->

### Business/Practical Interpretation

<!-- Non-technical explanation for decision-makers -->

## Final Conclusions and Recommendations

<!-- Overall evidence-based conclusions for Task 5 -->

\newpage

# Overall Summary and Conclusions

```{=html}
<!-- 
Provide a brief summary of key findings across all tasks.
Highlight the most important insights and recommendations.
-->
```

## Key Findings

<!-- Summarize main results from all tasks -->

## Limitations

<!-- Discuss any limitations of your analysis -->

## Future Directions

<!-- Suggest areas for further investigation -->

\newpage

# Appendix (Optional)

## Additional Code

```{r appendix-code}
# Any supplementary code that supports your analysis
# but is too detailed for the main sections

```

## Additional Tables and Figures

<!-- Include any supplementary materials here -->

\newpage

# References

```{=html}
<!-- 
If you use external sources, cite them appropriately.
You can use Quarto's citation features or list them manually.
-->
```

## Session Information

```{r session-info}
sessionInfo()
```

**Note:** This ensures reproducibility by documenting package versions used.
