---
title: "ETC2420/5242 Assignment 2"
subtitle: "Group [X] - [Your Group Name]"
author: 
  - "Student Name 1 (Student ID)"
  - "Student Name 2 (Student ID)"
  - "Student Name 3 (Student ID)"
  - "Student Name 4 (Student ID)"
date: "13 October 2025"
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    colorlinks: true
    geometry:
      - margin=2.5cm
    fontsize: 11pt
execute:
  echo: true
  warning: false
  message: false
  eval: true
---

# Initial Setup

```{r setup}
# Load required libraries
library(tidyverse)
library(gridExtra) 
library(broom)      
library(dplyr)

# Set seed for reproducibility
set.seed(24205242)  # Use your student ID

# Set knitr options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,
                      eval = TRUE, message = FALSE)

# Read data (adjust path as needed)
pedestrians <- read.csv("data/pedestrians.csv")
# Verify that the data exists 
```

\newpage

# Task 1: \[Task Title\]

## Introduction


## Data Exploration

```{r task1-exploration}
# Exploratory analysis code

```

<!-- Describe what you found in your exploration -->

## Analysis

### Technical Approach

<!-- Describe the statistical methods and techniques you will use -->

```{r task1-analysis}
# Main analysis code

```

### Results

<!-- Present your results with appropriate visualizations -->

```{r task1-plots}
# Create visualizations

```

**Figure 1.1:** \[Caption describing the plot\]

<!-- Interpret the results technically -->

## Interpretation

<!-- Non-technical explanation of your findings -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 1 -->

\newpage

# Task 2: \[20 marks\]

## Introduction

The task is to calculate the 90th percentile of the amount of traffic in each of the crossings (Southern Cross, Flinder's Street, QV Melbourne)

## Data Preparation

```{r task2-data-prep}
# Get each of the locations
qv_melbourne_traffic <- pedestrians[["qv_melbourne"]]
southern_cross_traffic <- pedestrians[["southern_cross"]]
flinders_street_traffic <- pedestrians[["flinders_street"]]
```

### Technical Approach

**Approach 1: Sample (Empirical) Quantile Method**

This involves bootstrapping, where many re-samples of the original data are created (with replacement) to emulate the variability we would see if we could repeatedly sample from the real population.

For each bootstrap sample, we calculate the 90th percentile—the value below which 90% of the observations in that specific sample fall. We repeat this process thousands of times, accumulating all of these 90th percentile values to create a distribution of the 90th percentile estimator.

We then find the 2.5th and 97.5th percentiles of this bootstrap distribution to construct a 95% confidence interval. This interval provides our estimate of the true population 90th percentile with 95% confidence, allowing us to determine the traffic level that each crossing must accommodate to ensure smooth pedestrian flow 90% of the time.

```{r task2-analysis}
# Approach 1: Sample (Empirical) Quantile Method
find_90th_percentile <- function(data, trials = 5000) {
  # Ensure data is a numeric vector
  if (!is.numeric(data)) {
    stop("Input must be a numeric vector.")
  }
  
  # Remove missing values
  x <- data[!is.na(data)]
  n <- length(x)
  if (n == 0) stop("No data points available after removing NA.")
  
  # Bootstrap resamples
  q_boot <- replicate(trials, {
    xb <- sample(x, size = n, replace = TRUE)
    as.numeric(quantile(xb, probs = 0.9, type = 7))
  })
  
  # 95% CI from bootstrap distribution
  ci <- quantile(q_boot, probs = c(0.025, 0.975))
  
  result <- list(
    ci_lower = unname(ci[1]),
    ci_upper = unname(ci[2])
  )
  
  return(result)
}
```

**Approach 2: Model Based Quantile**

### Results

```{r task2-results}
# Approach 1: Sample (Empirical) Quantile Method
qv_estimate_bootstrap <- find_90th_percentile(qv_melbourne_traffic)
flinders_estimate_bootstrap <- find_90th_percentile(flinders_street_traffic)
southern_estimate_bootstrap <- find_90th_percentile(southern_cross_traffic)

# Approach 2: Model Based Quantile

```

<!-- Technical interpretation of results -->

## Interpretation

<!-- Non-technical explanation for a general audience -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 2 -->

\newpage

# Task 3: \[Task Title\]

## Introduction

<!-- Overview of Task 3 -->

## Methodology

### Data Processing

```{r task3-data}
# Data processing code

```

### Statistical Methods

<!-- Explain the statistical techniques used -->

```{r task3-methods}
# Implementation of statistical methods

```

## Results and Visualizations

```{r task3-plots}
# Create visualizations

```

**Figure 3.1:** \[Caption\]

### Technical Analysis

<!-- Technical interpretation -->

### Non-Technical Summary

<!-- Explain findings in accessible language -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 3 -->

\newpage

# Task 4: \[Task Title\]

## Introduction

<!-- Overview of Task 4 -->

## Analysis Approach

### Data Exploration

```{r task4-exploration}
# Exploratory analysis

```

### Statistical Analysis

<!-- Describe your analytical approach -->

```{r task4-analysis}
# Main analysis code

```

## Results

```{r task4-results}
# Results and visualizations

```

**Figure 4.1:** \[Caption\]

### Technical Findings

<!-- Technical interpretation of results -->

### Practical Implications

<!-- Non-technical explanation and real-world implications -->

## Conclusions and Recommendations

<!-- Evidence-based conclusions for Task 4 -->

\newpage

# Task 5: \[Task Title\]

## Introduction

<!-- Overview of Task 5 -->

## Comprehensive Analysis

### Data Integration

```{r task5-data-integration}
# Combining and processing data

```

### Analytical Framework

<!-- Describe your comprehensive approach -->

```{r task5-framework}
# Implementation of analytical framework

```

## Results and Insights

```{r task5-results}
# Generate comprehensive results

```

**Figure 5.1:** \[Caption\]

### Technical Analysis

<!-- Detailed technical interpretation -->

### Business/Practical Interpretation

<!-- Non-technical explanation for decision-makers -->

## Final Conclusions and Recommendations

<!-- Overall evidence-based conclusions for Task 5 -->

\newpage

# Overall Summary and Conclusions

```{=html}
<!-- 
Provide a brief summary of key findings across all tasks.
Highlight the most important insights and recommendations.
-->
```

## Key Findings

<!-- Summarize main results from all tasks -->

## Limitations

<!-- Discuss any limitations of your analysis -->

## Future Directions

<!-- Suggest areas for further investigation -->

\newpage

# Appendix (Optional)

## Additional Code

```{r appendix-code}
# Any supplementary code that supports your analysis
# but is too detailed for the main sections

```

## Additional Tables and Figures

<!-- Include any supplementary materials here -->

\newpage

# References

```{=html}
<!-- 
If you use external sources, cite them appropriately.
You can use Quarto's citation features or list them manually.
-->
```

## Session Information

```{r session-info}
sessionInfo()
```

**Note:** This ensures reproducibility by documenting package versions used.
